---
title: "COVID-19 Anxiety Trends Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{COVID-19 Anxiety Trends Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(covidanxietytrends)
library(dplyr)
library(readr)
```

## Introduction
The `covidanxietytrends` package provides a set of functions for processing, analyzing, and visualizing the correlations between COVID-19 public health metrics and Anxiety-related Google search trends. This guide will show you through using this package for a complete analysis workflow, including data cleaning, visualization, feature analysis, and model preparation.

## Package Installation

You can install the development version from GitHub using:
```{r installation_github, eval=FALSE}
devtools::install_github("DSCI-310-2025/covidanxietytrends")
```
If you have cloned this repository locally, you can install it from the root folder using:
```{r package_installation, eval=FALSE}
devtools::install(".")
```
You can also check whether you have installed successfully in the Console. If it's installed, the output returns TRUE.
```{r installaion_check, eval=FALSE}
"covidanxietytrends" %in% installed.packages()[, "Package"]
```


## Create example data
We will start by creating a small simulated dataset

```{r covid_df-setup, include=FALSE}
set.seed(310)

covid_df <- data.frame(
  date = seq.Date(as.Date("2020-01-01"), by = "day", length.out = 30),
  search_trends_anxiety = rnorm(30),
  new_hospitalized_patients = rnorm(30),
  new_confirmed = rnorm(30),
  new_intensive_care_patients = rnorm(30),
  new_persons_vaccinated = rnorm(30)
)

```

```{r}
# Save the above simulated data to a temporary CSV file
write_csv(covid_df, "covid_data.csv")
```

```{r}
dim(covid_df)
head(covid_df)
```

## Load data
The load_data() function takes the COVID-19 raw tabular file path and loads it onto the workspace.
```{r, eval=FALSE}
covid_df <- load_data("covid_data.csv")

# Clean up the temporary file
unlink("covid_data.csv")
```

## Clean using the package function
The clean_covid_data() function prepares your raw COVID-19 dataset by handling missing values and formatting dates:
```{r, eval=FALSE}
clean_data <- clean_covid_data(covid_df)
head(clean_data)
```

## Explore the numeric summaries
The eda_tbl() function provides quick numeric summaries of key variables:
```{r, eval=FALSE}
eda_tbl(clean_data)
```

## Visualize the anxiety trends
The eda_viz() function creates time series visualizations of anxiety trends versus COVID-19 metrics:
```{r, eval=FALSE}
eda_viz(clean_data)
```

## Analyze variable relationships
The eda_viz_pairplot() function generates pairwise relationship visualizations:
```{r, eval=FALSE}
eda_viz_pairplot(clean_data)
```

## Feature Selections 
the feature_selection() function identifies the most significant COVID-19 metrics:
```{r, eval=FALSE}
selected_vars <- feature_selection(clean_data)
selected_vars$selected_features
```

## Build predictive models
The make_final_lm_model() function creates linear models for analysis:
```{r, eval=FALSE}
model <- make_final_lm_model(clean_data)
```

## View the model results
The results_lm_coef() function displays model coefficients:
```{r, eval=FALSE}
results_lm_coef(model)
```

## Generate predictions
The model_predictions() function creates test predictions:
```{r, eval=FALSE}
predictions <- model_predictions(model, new_data = clean_data)
```

## In Summary
The covidanxietytrends package provides a complete toolkit for analyzing COVID-19 and anxiety trend relationships:

1. Clean and prepare COVID-19 datasets
2. Generate exploratory visualizations
3. Identify significant pandemic indicators
4. Build and evaluate predictive models
5. Create actionable predictions

utils::globalVariables(names = c(
  "search_trends_anxiety",
  "new_persons_vaccinated",
  "new_hospitalized_patients",
  "new_confirmed",
  "new_intensive_care_patients"
))



